\addcontentsline{toc}{chapter}{Bibliography}
\begin{thebibliography}{999}

% stile: Autori (normale): titolo (corsivo), data (normale). Sito web (normale)
      % \bibitem[]{} \textbf{}: \emph{}, .
%______________________________________________________________________________
				%cap1
		\bibitem{PDG} C. Patrignani et al. (Particle Data Group), Chin. Phys. C, 40, 100001 (2016) and 2017 update.
		\bibitem{HalzenMartin} Halzen and Martin, \emph{Quarks and Leptons: An Introductory Course in Modern Particle Physics}, John Wiley \& Sons (1984).
		\bibitem{Peskin} M.E.Peskin and D.V.Schroeder, \emph{An Introduction To Quantum Field Theory}, Addison-Wesley, 1995.
		\bibitem{Maggiore} M.Maggiore, \emph{A Modern Introduction to Quantum Filed Theory}, Oxford University Press, 2004.
		\bibitem{QCD} A.Pich, \emph{The standard model of electroweak interactions}, arXiv:hep-ph/0502010v,  2005.
		\bibitem{Wboson}  UA1 Collaboration, \emph{Experimental observation of isolated large transverse energy electrons with associated missing energy at $sqrt{s}=540~GeV$.}
		\bibitem{Zboson} UA1 Collaboration, \emph{Experimental observation of lepton pairs of invariant mass around $95~GeV/c^{2}$ at the CERN SPS collider.}
		\bibitem{SU2_Hmechanism} S. Weinberg, \emph{A model of leptons}, Phys. Rev. Lett. 19 (1967) 1264.
%		\bibtiem{MassZ}  The LEP Collaborations ALEPH, DELPHI, L3 and OPAL and the LEP Electroweak Working Group, arXiv:hep-ex/0612034; http://www.cern.ch/LEPEWWG/.
%		\bibtiem{MassW} The ALEPH, DELPHI, L3, OPAL and SLD Collaborations, the LEP Electroweak Working Group and the SLD Electroweak and Heavy Flavour Groups, Phys. Rept. 427 (2006) 257.
		\bibitem{muLifetime} MuLan Collaboration, \emph{Improved Measurement of the Positive Muon Lifetime and Determination of the Fermi Constant}, Phys.Rev.Lett.99:032001,2007, 	arXiv:0704.1981.
		\bibitem{ALTAS_H} ATLAS Collaboration, \emph{Observation of a new particle in the search for the Standard Model Higgs boson with the ATLAS detector at the LHC},  Phys.Lett. B716 (2012), pp. 1-29, DOI: 	10.1016/j.physletb.2012.08.020.
		\bibitem{CMS_H} CMS Collaboration, \emph{Observation of a new boson at a mass of 125 GeV with the CMS experiment at the LHC}, Physics Letters B716 (2012), pp. 30-61. DOI:   http://dx.DOI.org/10.1016/j.physletb.2012.08.021 .
		\bibitem{HiggsProduction} LHC Higgs Cross Section Working Group, \\https://twiki.cern.ch/twiki/bin/view/LHCPhysics/LHCHXSWG.
		\bibitem{ggF_value} D. de Florian et al., [LHC Higgs Cross Section Working Group], CERN-2017-002-M, arXiv:1610.07922[hep-ph] (2016).
		\bibitem{BR_1} S. Heinemeyer et al., [LHC Higgs Cross Section Working Group], CERN?2013?004, arXiv:1307.1347 [hep-ph] (2013).
		\bibitem{BR_2} D. de Florian et al., [LHC Higgs Cross Section Working Group], CERN?2017?002-M, arXiv:1610.07922[hep-ph] (2016).
		\bibitem{LHC} Lyndon Evans and Philip Bryant, [LHC Machine], 1748-0221-3-08-S08001, Journal of Instrumentation (2008), http://stacks.iop.org/1748-0221/3/i=08/a=S08001
		\bibitem{CMS_Detector} CMS Collaboration, [The Compact Muon Solenoid technical proposal], CERN-LHCC-94-38, http://cdsweb.cern.ch/record/290969
		\bibitem{Tracker_1}  CMS Collaboration, [The CMS tracker system project: technical design report], CERN-LHCC-98-006, http://cdsweb.cern.ch/record/368412.		\bibitem{Tracker_2}  CMS Collaboration, [The CMS tracker: addendum to the technical design report] CERN-LHCC-2000-016, http://cdsweb.cern.ch/record/490194.
		\bibitem{New_Pixel_Detector} Anirban Saha, [Phase 1 upgrade of the CMS pixel detector], Journal of Instrumentation (2017), http://stacks.iop.org/1748-0221/12/i=02
		\bibitem{PbWO4} PARTICLE DATA GROUP Collaboration, S. Eidelman et al., [Review of particle physics] Phys. Lett. B 592 (2004) 1.
		\bibitem{HCAL}  CMS Collaboration, [The hadron calorimeter project: technical design report], CERN-LHCC-97-031, http://cdsweb.cern.ch/record/357153.
		\bibitem{muon} CMS Collaboration, [The CMS muon project, technical design report], CERN-LHCC-97-032, http://cdsweb.cern.ch/record/343814.
		\bibitem{GEM} CMS Collaboration, [CMS TECHNICAL DESIGN REPORT FOR THE MUON ENDCAP GEM UPGRADE], CERN-LHCC-2015-012, https://cds.cern.ch/record/2021453/files/CMS-TDR-013.pdf
		\bibitem{L1} CMS Collaboration, [CMS. The TriDAS project. Technical design report, vol. 1: The trigger systems.] In: (2000).
		\bibitem{HLT} CMS Collaboration, [CMS The TriDAS Project: Technical Design Report, Volume 2: Data Acquisition and High-Level Trigger. CMS trigger and data- acquisition project. Technical Design Report CMS]. Geneva: CERN, 2002. url: http://cds.cern.ch/record/578006.
				
           	  
	 
	 \end{thebibliography}
\clearpage{\pagestyle{empty}\cleardoublepage}